DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-03 paper/overview.tex
use hyperref package

Note that although the steering angle output of the network $angle$ is
a continuous real value, the RC car platform we used unfortunately
only supports three discrete angles---left (-30$^{\circ}$), center
(0$^{\circ}$), and right (+30$^{\circ}$)---as control
inputs. Currently, we approximate the network generated real-valued
angle to the closest one of the three angles. Although this may
introduce inaccuracy in control.
In the future, we plan to use different (more expensive) RC car
platforms that can precisely control the car's steering angle. We
would like to stress, however, that the use of different RC car
platforms has no impact in terms of computational 
aspects of the system, and that our main focus of this study is
not in improving network accuracy but in closely replicating the
DAVE-2's network architecture and its real-time characteristics.

Nevertheless, the trained model was still able to achieve reasonable a
degree of accuracy, successfully navigating several different tracks 
we trained. A collection of self-driving videos of the DeepPicar can
be found at: \url{https://github.com/heechul/picar/videos}.

>>>>

Note that although the steering angle output of the network $angle$ is
a continuous real value, the RC car platform we used unfortunately
only supports three discrete angles---left (-30$^{\circ}$), center
(0$^{\circ}$), and right (+30$^{\circ}$)---as control
inputs. Currently, we approximate the network generated real-valued
angle to the closest one of the three angles, which may
introduce inaccuracy in control.
In the future, we plan to use different (more expensive) RC car
platforms that can precisely control the car's steering angle. We
would like to stress, however, that the use of different RC car
platforms has no impact in terms of computational 
aspects of the system, and that our main focus of this study is
not in improving network accuracy but in closely replicating the
DAVE-2's network architecture and its real-time characteristics.

Nevertheless, the trained models were still able to achieve reasonable
a degree of accuracy, successfully navigating several different tracks 
we trained. The source code, build instruction, and a collection of
self-driving videos of the DeepPicar can be found at:
\url{https://github.com/heechul/picar}.
%% \begin{center}
%% \end{center}
